Learning Libraries of Subroutines for Neurally--Guided Bayesian Program Learning

### 2018-05-17 nips_2018.tex
change experiment-related section titles

\section{Sequence manipulating programs}\label{sequences}
We apply \system to list processing (Section~\ref{listSection}) and text editing (Section~\ref{textSection}).
For both these domains we use a bidirectional GRU~\cite{cho2014learning} for
the recognition model, and initially provide the system with a generic set
of list processing primitives:
\code{foldr}, \code{unfold}, \code{if}, \code{map}, \code{length},
\code{index}, \code{=}, \code{+}, \code{-}, \code{0}, \code{1}, \code{cons},
\code{car}, \code{cdr}, \code{nil}, and \code{is-nil}.

@@

\subsection{Quantitative Results}\label{quantitative}

>>>>

\section{Sequence Manipulation: Domains from generic primitives}\label{sequences}
We apply \system to list processing (Section~\ref{listSection}) and text editing (Section~\ref{textSection}).
For both these domains we use a bidirectional GRU~\cite{cho2014learning} for
the recognition model, and initially provide the system with a generic set
of list processing primitives:
\code{foldr}, \code{unfold}, \code{if}, \code{map}, \code{length},
\code{index}, \code{=}, \code{+}, \code{-}, \code{0}, \code{1}, \code{cons},
\code{car}, \code{cdr}, \code{nil}, and \code{is-nil}.

@@

\section{Quantitative Results}\label{quantitative}
